SIMD-vectorized Chemical Source Term Evaluation

### 2017-02-26 paper.tex
update wording

However, in computing the net ROP of reaction $i$ for state $j$ from the forward and reverse ROP: $R_{ij} = R_{ij}^{\prime} - R_{ij}^{\prime\prime}$, accuracy can easily be lost as the net ROP may be---particularly near chemical equilibrium---many orders of magnitude smaller than the forward or reverse rates.
To quantify this phenomena, the error in forward ROP is first defined as:
\begin{equation}
\varepsilon^{\prime}_{ij} = \left\lvert R_{ij}^{\prime} - R_{ij,\text{CT}}^{\prime} \right\rvert
\end{equation}
and the error in reverse ROP $\varepsilon^{\prime\prime}_{ij}$ can be defined analogously.
Finally, for the reaction $i^{*}$ and state $j^{*}$ that result in the largest error in net ROP, i.e. $E_{R}$, an estimate of the percent error attributable to floating point error accumulation from the forward and reverse ROPs can be obtained as:
\begin{equation}
E_{\varepsilon} = 100\times\frac{\max(\varepsilon^{\prime}_{i^{*}j^{*}}\text{, }\varepsilon^{\prime\prime}_{i^{*}j^{*}})}{R_{i^{*}j^{*},\text{CT}}} \si{\percent}
\end{equation}
If this estimate is near \SI{100}{\percent}, it indicates that the maximum error in forward or reverse ROPs are of a similar magnitude to the net ROP, hence the error in net ROP would be expected to be large in this case.

>>>>

However, in computing the net ROP of reaction $i$ for state $j$ from the forward and reverse ROP: $R_{ij} = R_{ij}^{\prime} - R_{ij}^{\prime\prime}$, accuracy can easily be lost as the net ROP may be---particularly near chemical equilibrium---many orders of magnitude smaller than the forward or reverse rates.
To quantify this phenomena, the error in forward ROP is first defined as:
\begin{equation}
\varepsilon^{\prime}_{ij} = \left\lvert R_{ij}^{\prime} - R_{ij,\text{CT}}^{\prime} \right\rvert
\end{equation}
and the error in reverse ROP $\varepsilon^{\prime\prime}_{ij}$ can be defined analogously.
Finally, for the reaction $i^{*}$ and state $j^{*}$ that result in the largest error in net ROP, i.e. $E_{R}$, an estimate of the percent error attributable to floating point error accumulation from the forward and reverse ROPs can be obtained as:
\begin{equation}
E_{\varepsilon} = 100\times\frac{\max(\varepsilon^{\prime}_{i^{*}j^{*}}\text{, }\varepsilon^{\prime\prime}_{i^{*}j^{*}})}{R_{i^{*}j^{*},\text{CT}}} \si{\percent}
\end{equation}
If this estimate is near \SI{100}{\percent}, it indicates that the maximum error in forward or reverse ROPs are of a similar magnitude to the net ROP, hence the error in net ROP is expected be large in this case.
